Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations

### 2018-07-20 paper.tex
new figures

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{}
\author{Baptiste Mouginot, Kathryn Mummah, Paul P.H.  Wilson}

@@

\usepackage[acronym]{glossaries}
\newacronym{UOX}{UOX}{uranium oxide fuel}
\newacronym{MOX}{MOX}{mixed oxide fuel}
\newacronym{LWR}{LWR}{light water reactor}
\newacronym{SFR}{SFR}{fast breeder reactor}

@@

\subsection{The Fuel Cycle Scenario}
For demonstration purposes, a simple commercial fuel cycle transition is used,
inspired from the EG23 fuel cycle
of the Nuclear Fuel Cycle Evaluation and Screening Report\cite{ES}.
Pictured in Figure \ref{fig:cycle}, this is a
transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a
\gls{SFR} fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth
of the nuclear generated power (Figure \ref{fig:power}).
\begin{figure}[b] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Simplified representation of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}

@@

For each of the parameters in Table \ref{tab:package_uncertainty}, a set of
199 simulations was performed with only that parameter being randomly varied.
An additional set of 199 simulations was performed in which all five
parameters are randomly varied.  A reference simulation was performed
with all five parameters fixed at the mean value.

@@

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.3]{unat_uncer}
    \caption{Relative uncertainty of the cumulative natural uranium consumption, including
      individual contributions from each varied parameter.}\label{fig:unatr_uncer}
\end{figure}
The relative uncertainty of the total uranium consumption starts at about
$5.5\%$ a slowly drops and stabilize around $3\%$.

@@

\subsection{Fissile Inventory}
The fissile inventory corresponds to the amount of separated fissile material waiting to
be blended with natural uranium in order to produce the \gls{SFR}-\gls{MOX} fuel.

@@

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.16]{used_fuel}
    \caption{Used fuel inventory, corresponding to the amount of used
    \glspl{LWR} and \glspl{SFR} fuel, cooled and waiting to be reprocessed.}
    \label{fig:used_fuel}
\end{figure}
Between year 90 and 120, the \gls{SFR} deployment speed increases; it has to
compensate the non-replacement of the decommissioned \glspl{LWR} as well as
follow the growing power demand.  During this period the needs in plutonium are higher
than its production, explaining the observed decrease of the total amount, and
the increase associated relative uncertainty.

@@

>>>>

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Assessing Material Inventory Uncertainties in Integrated Fuel Cycle Simulations}
\author{Baptiste Mouginot, Kathryn Mummah, Paul P.H.  Wilson}

@@

\usepackage[acronym]{glossaries}
\newacronym{UOX}{UOX}{uranium oxide fuel}
\newacronym{MOX}{MOX}{mixed oxide fuel}
\newacronym{LWR}{LWR}{light water reactor}
\newacronym{SFR}{SFR}{fast breeder reactor}
\newacronym{OFAT}{OFAT}{one-factor-at-a-time}

@@

\subsection{The Fuel Cycle Scenario}

For demonstration purposes, a simple commercial fuel cycle transition is used,
inspired from the EG23 fuel cycle of the Nuclear Fuel Cycle Evaluation and
Screening Report\cite{ES}.  Pictured in Figure \ref{fig:cycle}, this is a
transition from a \gls{LWR} fleet loaded with \gls{UOX} fuel to a \gls{SFR}
fleet loaded \gls{MOX} fuel, considering a $1\%/$y growth of the nuclear
generated power (Figure \ref{fig:power}).

\begin{figure}[b] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[scale=0.31]{cycle.png}
  \caption{Simplified representation of the material flow between the different facilities,
  with each operational parameter associated with an
  uncertainty labeled in green.}\label{fig:cycle}
\end{figure}

@@

For each of the parameters in Table \ref{tab:package_uncertainty}, a set of 199
simulations was performed with only that parameter being randomly varied.  An
additional set of 199 simulations was performed in which all five parameters are
randomly varied, using \gls{OFAT} method.  A reference simulation was performed
with all five parameters fixed at the mean value.

@@

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.3]{unat_uncer}
    \caption{Relative uncertainty of the cumulative natural uranium consumption, including
      individual contributions from each varied parameter.}\label{fig:unatr_uncer}
\end{figure}

The relative uncertainty of the total uranium consumption starts at about
$7\%$ a slowly drops and stabilize around $3\%$.

@@

\subsection{Fissile Inventory}

The fissile inventory corresponds to the amount of separated fissile material
waiting to be blended with natural uranium in order to produce the
\gls{SFR}-\gls{MOX} fuel.

@@

\begin{figure}[t] % replace 't' with 'b' to force it to be on the bottom
    \centering
    \includegraphics[scale=0.16]{used_fuel}
    \caption{Used fuel inventory, corresponding to the amount of used
    \glspl{LWR} and \glspl{SFR} fuel, cooled and waiting to be reprocessed.}
    \label{fig:used_fuel}
\end{figure}

Between year 90 and 120, the \gls{SFR} deployment speed increases; it has to
compensate the non-replacement of the decommissioned \glspl{LWR} as well as
follow the growing power demand.  During this period the needs in plutonium are
higher than its production, explaining the observed decrease of the total
amount, and the increase associated relative uncertainty.

@@

Around the year 70, it is possible to observe the relative uncertainty related
to cycle time being larger than the overall relative uncertainty. This effect is
directly related to the \gls{OFAT} method used to estimate the individual
uncertainty contribution. While allowing a quick access to the individual
contribution, the \gls{OFAT} method does not capture coupling effect between the
different parameters.
